---
title: "My R Markdown Notebook"
author: 
    - Rahul Bhadani^[The University of Arizona, rahulbhadani@email.arizona.edu]
date: "`r format(Sys.time(), '%d %B %Y')`"
bibliography: citations.bib
output:
  
  html_notebook: default
  html_document:
    df_print: paged
  pdf_document:
    citation_package: natbib
    keep_tex: yes
    number_sections: yes
classoption:
- onecolumn
header-includes:
- \usepackage[none]{hyphenat}
- \usepackage{physics}
- \graphicspath{ {figures/} }
- \usepackage{color}
- \definecolor{ocre}{RGB}{243,102,25}
- \usepackage[font={color=ocre,bf},labelfont=bf]{caption}
- \usepackage{hyperref}
- \hypersetup{colorlinks=true,citecolor=blue}
- \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
keep_tex: yes
abstract: This is my abstract
---
https://towardsdatascience.com/powerful-r-markdown-for-python-users-f20607f24f08

Using R Markdown to generate rich PDFs
R Markdown uses knitr, which is a dynamic report generation engine for the R language. It can generate a fully reproducible notebook in multiple formats such as PDF and HTML. Knitr engine incorporates various languages such as R, Python, Bash, and SQL. For this article, I am limiting myself to Python and Bash.
To appreciate the article fully and follow along, please install R Studio and R. I am using Ubuntu OS for my examples. However, all examples should work with Windows or Mac with some extra steps that I won’t go into detail about in this article.
Generating LaTeX Doc
Once you have installed R language and R Studio, click to create a new R Notebook.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(reticulate)
use_condaenv("r-reticulate")
#py_install("pandas", pip = TRUE)
py_module_available("pandas")
#py_install("seaborn", pip = TRUE)
py_module_available("seaborn")
```

```{r, echo=T,eval=T,warning=FALSE, fig.height = 4, fig.width = 5}
library('nloptr')
hn <- function(x, n)
{
    hret <- 0
    if (n == 0)
    {
       hret <- x + 2*x
    }
    else
    {
       hret <- x - 2*x
    }
    return (hret)
}
```
```{python}
libraimport pandas as pd
import seaborn as sns
iris = sns.load_dataset('iris')
iris.head()
iris['sepal_length'].plot()
```
Adding Python code in R Markdown
To add python code to the R Markdown file, add the following code snippets:

With engine.path , I am specifying where to look for a python executable to run the python code snippet. Upon running the above code, I can see the following content in my PDF file:

```{python, engine.path =  "/home/oscar/.local/share/r-miniconda/envs/r-reticulate/bin/conda-env", fig.height = 3, fig.width = 6}
import pandas as pd
import seaborn as sns
iris = sns.load_dataset('iris')
iris.head()
iris['sepal_length'].plot()
```

Executing bash commands in R Markdown
To execute a bash command, you will need to add the following code snippet:
```{bash, engine.opts='-l'}
source ~/.bashrc
source /opt/ros/melodic/setup.bash
source ~/catkin_ws/devel/setup.bash
pwd
ls
```